---
title: "p8105_hw5_ms5965"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(ggplot2)

knitr::opts_chunk$set(
	fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Reading in the data.

```{r}
homicide_df = 
  read_csv("homocide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```


```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```


```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```


```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


## Problem 2

```{r, include = FALSE}
path_df = 
  tibble(
    path = list.files("study_data"),
  ) %>% 
  mutate(
    path = str_c("study_data/", path)) 

df = map_dfr(path_df$path, read_csv)

read_csv(path_df$path)
```


```{r}
data_dir = "study_data" %>% 
  fs::dir_ls() %>% 
  map_dfr(read_csv, .id = "file.ID")
 
clean_df = 
  data_dir %>% 
   separate(
    file.ID,
    into = c(NA, "arm_id"),
    sep = "/") %>% 
  separate(
    arm_id,
    into = c("arm_id", NA),
    sep = "\\.") %>% 
  separate(
    arm_id,
    into = c("arm", "id"),
    sep = "_") %>% 
  
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observations",
    names_prefix = "week_"
  ) %>% 
  mutate(week = as.numeric(week))
```


```{r, plot}
plot = 
  clean_df %>% 
  ggplot(aes(x = week, y = observations, group = arm, color = arm)) +
  geom_line() + 
  stat_smooth(aes(group = 1), geom = "point", fun.y = mean, shape = 10, size = 1) + 
  facet_grid(. ~ arm) 

plot
```

The experiment group shows an increasing trend while the control group stays more stable over time. 


## Problem 3

```{r}
sim_mean_sd = function(n, mean, sd) {
 
  sim_data = tibble(
    x = rnorm(n, mean, sd)
      ) %>% 
    t.test(
      alternative = 'two.sided', 
      paired = FALSE, 
      conf.level = 0.95
      ) %>% 
    broom::tidy()
  
 }
```

For mean = 0

```{r}
sim_results = 
    rerun(5000, sim_mean_sd(30, 0, 5)) %>% 
    bind_rows()
```

For all means:

```{r}
sim_plot_data =
    tibble(
      mean_list = c(0, 1, 2, 3, 4, 5, 6)
    ) %>% 
  mutate(
    output_lists = map(.x = mean_list, ~rerun(5000, sim_mean_sd(30, mean = .x, sd = 5))),
    estimate_dfs = map(output_lists, bind_rows)
    ) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs)

```

### First plot

```{r}
plot_A = 
  sim_plot_data %>% 
  group_by(mean_list) %>% 
  summarize(
        reject = sum(p.value <= 0.05),
        count = n()
      ) %>% 
      mutate(
        prop = reject/count
      ) %>% 
    ggplot(aes(x = mean_list, y = prop)) +
        geom_point() +
        geom_line() +
    labs(
    title = "Power of the Test", 
    x = "Effect Size", 
    y = "Proportion of rejects"
  ) 

plot_A

```

As the effect size increases, the proportion of rejects increases (power increases) - it plateaus at effect sizes of 4, 5 & 6. 

### Second Plot

```{r}
plot_B = 
  sim_plot_data %>% 
  group_by(mean_list) %>% 
  summarize(
    avg_mu = mean(estimate)
  ) %>% 
  ggplot(aes(x = mean_list, y = avg_mu)) +
  geom_point() + 
  geom_line() +
  labs(
    y = "Average Estimates", 
    x = "Effect Size"
  )

plot_B
```


```{r}
plot_C = 
  sim_plot_data %>% 
  filter(p.value <= 0.05) %>% 
  group_by(mean_list) %>% 
  summarize(
    avg_mu = mean(estimate)
  ) %>% 
  ggplot(aes(x = mean_list, y = avg_mu)) +
  geom_point() + 
  geom_line() +
  labs(
    title = "Samples for which the null was rejected",
    y = "Average Estimates", 
    x = "Effect Size"
  ) 

plot_C
```

The sample average of μ^ across tests for which the null is rejected approximately equal to the true value of μ for mu values of 3 or greater. For smaller values there's a difference; the average is double for samples for which the null was rejected. 

